EUC_PVE

### 2014-07-28 markdowns/master.rmd
failed attempt at getting rootshoot to work with markdown

```{r root:shoot plots }
#source("master_scripts/rootshoot_plotting.R")
```

@@

Predicted responses of Amax on a mass basis to leaf starch and N levels
```{r Amass vs TNC and N}
source(("master_scripts/photochem_predict.R")
```

>>>>

```{r root:shoot plots }
source("master_scripts/rootshoot_plotting.R")
```

@@

Predicted responses of Amax on a mass basis to leaf starch and N levels
```{r Amass vs TNC and N}
#source(("master_scripts/photochem_predict.R")
```
